---
title: "Bayesian Statistics"
author: "Mauricio Matoma"
format: gfm
editor: visual
---

My first simulation

```{r, message=FALSE}
set.seed(20202020)
boxes <- sample(c("GG", "SS","GS"),
                size=10^5, replace = TRUE,
                prob=c(1/3,1/3,1/3))
table(boxes)/10^5
```

Each box appears with about 1/3 probability as expected. Now, let’s simulate what dagger they will see first.

```{r, message=FALSE}
dagger <- rbinom(10^5, size = 1, prob=c(1,.5,0)[as.numeric(as.factor(boxes))])
```

The elements of the vector ‘dagger’ take the value of ‘0’ for silver and ‘1’ for gold. The probability of golden dagger depends on the box. If you are unsure about any piece of the code, go deeper. Check:

```{r, message=FALSE}
boxes[1:5]#Factores de ejemplo (contenido de cajas)
as.factor(boxes)[1:5] #Levels de esas cajas
as.numeric(as.factor(boxes)[1:5]) #Convertilas en valores numéricos ("discretos")
c(1,.5,0)[as.numeric(as.factor(boxes))[1:5]] #Los convierte en numéricos "continuos" (probabilidad)
```

and see what changes.

What is the frequency distribution of ones (gold dagger seen first) and zeroes (silver dagger seen first)?

```{r, message=FALSE}
table(dagger)/10^5
```

Pretty much 50/50. As expected.

Final.
